---
title: "[Tool Demo] `paperboy` --- A Collection of News Media Scrapers"
author: Johannes B. Gruber
presentation: ICA25 --- 2025-06-15
---

![](paperboy_logo.svg)

# Philosphy

The philosophy of the `R` package paperboy is that the package is a repository for web scraping scripts for news media sites, with advanced features for quick data retrieval --- even for content behind log-ins or anti-scraping measures.

Goal: bring together Developers and Users of news web-scrapers

# Installation

```{r}
remotes::install_github("JBGruber/paperboy")
```

# For Users
## Single Link Examples

```{r sinlge-1}
library(paperboy)
cnn_df <- pb_deliver("https://bit.ly/47bPVWP")
dplyr::glimpse(cnn_df)
```

- URL is automatically unshortened
- *CNN* parser is selected
- Content is cleanly parsed

```{r sinlge-2}
mbpassion_df <- pb_deliver("https://bit.ly/3MqSnk7")
dplyr::glimpse(mbpassion_df)
```

- URL is automatically unshortened
- **No** parser for *Mercedes-Benz Passion* is available, but fallback on generic parser
- Content is cleanly parsed

## Rehydration Example

```{r}
library(httr2)
test_data <- request("https://search.mediacloud.org/api/") |>
  req_url_path_append("search/story-list") |>
  req_headers(
    Authorization = paste("Token", Sys.getenv("MC_TOKEN")),
    Accept = "application/json"
  ) |>
  req_url_query(
    q = "harris",
    start = "2024-01-01",
    ss = 107736L # source ID of huffpost.com
  ) |>
  req_perform() |>
  resp_body_json() |>
  purrr::pluck("stories") |>
  dplyr::bind_rows()
dplyr::glimpse(test_data)
```

```{r}
saveRDS(test_data, "test_data.rds")
test_data <- readRDS("test_data.rds")
```


```{r}
test_data_hydrated <- pb_collect(
  test_data$url,
  host_con = 100
)
```

- for many URLs it often makes sense first collect the data before parsing
- it can also make sense to save this raw html for archival
- if you were surprised how fast this was, you were right:
    - `paperboy` collects 100 html pages at once
    - for 1000 pages this takes ~7 at my home

```{r}
test_data_hydrated_parsed <- pb_deliver(test_data_hydrated[1:200, ])
dplyr::glimpse(test_data_hydrated_parsed)
```

```{r}
#| message: false
test_data_hydrated_parsed <- readRDS("data/test_data_hydrated_parsed.rds")
library(quanteda)
corpus(test_data_hydrated_parsed) |>
  tokens(
    remove_punct = TRUE,
    remove_symbols = TRUE,
    remove_numbers = TRUE
  ) |>
  dfm() |>
  dfm_remove(stopwords("en")) |>
  topfeatures()
```

## Using cookies

```{r}
URL <- "https://www.zeit.de/arbeit/2024-10/viertagewoche-arbeitszeit-umsatz-effizienz-deutschland"

library(rvest)
html <- read_html(URL)
text <- html |>
  html_elements(".article-body p") |>
  html_text2() |>
  paste(collapse = "\n")
nchar(text)
```

- the article above is behind a paywall
- I use rvest here to show that the short snippet is not `paperboy`'s fault

```{r}
cookiemonster::add_cookies("zeit_cookies.txt")
content_df <- pb_collect(URL, use_cookies = TRUE)
```

- we can use one of my other packages, `cookiemonster`, to read my log in cookies into R (I'm subscribed to Zeit.de)

```{r}
html2 <- read_html(as.character(content_df$content_raw))
text2 <- html2 |>
  html_elements(".article-body p") |>
  html_text2() |>
  paste(collapse = "\n")
nchar(text2)
```

- the content from `pb_collect` is compatible with rvest, so we can compare
- with the right cookies, the website delivers the full content


# For Developers

```{r}
pb_find_rss("https://www.denverpost.com") |>
  View()
```

- For testing purposes, I want to know the RSS location

```{r}
rss <- "https://denverpost.com/feed"
test_df <- pb_collect(rss)
dplyr::glimpse(test_df)
```

```{r}
use_new_parser(
  x = "https://www.denverpost.com/2025/06/13/no-kings-protest-colorado-donald-trump/",
  author = "JBGruber",
  rss = rss
)
```

- the usethis inspired function guides you through making a new parser

```{r}
pb_inspect(test_df)
```

- to find the appropriate css tags, we inspect the collected html site
- running use_new_parser again tests the new parser on fresh data

```{r}
use_new_parser(
  x = "https://www.denverpost.com/2025/06/13/no-kings-protest-colorado-donald-trump/",
  author = "JBGruber",
  rss = rss,
  test_data = test_df
)
```

All done! Another site can be added!

# How can you help?

- cite the package
- let me know if you have issues
- become a contributor/co-author!
- advise me on an incentive structure

